Formalizing Stack Safety as a Security Property

### 2021-07-08 submission3/main.tex
Remove comment

As for criterion (5), we have demonstrated that our approach extends
to coroutines, a first step towards multithreading.
Dynamic code generation is more challenging, but StkTokens does not yet
handle this either.
StkTokens is specifically set up to address criterion (3), while this is not
a goal of our work. We do agree that criterion (2) is important;
demonstrating it for our proposal remains future work.

>>>>

As for criterion (5), we have demonstrated that our approach extends to
coroutines, a first step towards multithreading.  Dynamic code generation is
more challenging, but StkTokens does not yet handle this either.  StkTokens
is specifically set up to address criterion (3), while this is not a goal of
our work. We agree that criterion (2), usefulness of the safety criterion
for carrying out formal proofs (about individual programs), is important;
demonstrating it for our proposal remains future work.  Instead, we have
chosen to focus on property-based random testing as a methodology for
validating enforcement mechanisms.
